Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-09-01 Scripts/Initial_Analysis.Rmd
Analysis done

# Fix coordinate system and re-name biomes
Biogeo_reg <- suppressWarnings(Biogeo_reg[order(Biogeo_reg$lat, rev(Biogeo_reg$lon),decreasing=TRUE), ]) %>% 
  mutate(index = seq(1,259200,1)) %>% 
  mutate(
    # biome = ifelse(biome2 == 1, "c_tropical",
    #                ifelse(biome2 == 2,"c_temperate",
    #                       ifelse(biome2 == 3, "c_polar",
    #                              ifelse(biome2 == 4, "o_tropical",
    #                                     ifelse(biome2 == 5, "o_temperate",
    #                                            ifelse(biome2 == 6, "o_polar",
    #                                                   biome2
    #                                            )
    #                                     )
    #                              ) 
    #                       )
    #                )
    # ),
    biome = ifelse(biome2 %in% c(1,4), "tropical",
                   ifelse(biome2  %in% c(2,5),"temperate",
                          ifelse(biome2  %in% c(3,6), "polar",
                                 biome2)
                   )
    )
    ) %>% 
  filter(biome2 != "NaN")

@@

#Table for supplements
M9_sum %>% 
  tidy() %>% 
  # filter(p.value < 0.05) %>% 
  # mutate(p.value = ifelse(p.value < 0.001,0.001,round(p.value,3))) %>% 
  # stargazer(title = "Multiple regression results for time of emergence of Transboundary stocks. Only showing explanatory variables. The model significantly predicts time of emergencec (F(31,5270) = 15.38, p < 0.001, R2 = 0.06).",
            # align=TRUE)
  # knitr::kable() %>% 
  write_csv(.,
            "./Tables/mlr_result_sup.csv")
```

>>>>

# Fix coordinate system and re-name biomes
Biogeo_reg <- suppressWarnings(Biogeo_reg[order(Biogeo_reg$lat, rev(Biogeo_reg$lon),decreasing=TRUE), ]) %>% 
  mutate(index = seq(1,259200,1)) %>% 
  mutate(
    biome = ifelse(biome2 %in% c(1,4), "tropical",
                   ifelse(biome2  %in% c(2,5),"temperate",
                          ifelse(biome2  %in% c(3,6), "polar",
                                 biome2)
                   )
    )
    ) %>% 
  filter(biome2 != "NaN")

@@

#Table for supplements
M9_sum %>% 
  tidy() %>% 
  # filter(p.value < 0.05) %>% 
  # mutate(p.value = ifelse(p.value < 0.001,0.001,round(p.value,3))) %>% 
  # stargazer(title = "Multiple regression results for time of emergence of Transboundary stocks. Only showing explanatory variables. The model significantly predicts time of emergencec (F(18,6155) = 20.68, p < 0.001, R2 = 0.05).",
            # align=TRUE)
  # knitr::kable() %>% 
  write_csv(.,
            "./Tables/mlr_result_sup.csv")
```
